---
title: "p8105_hw6_st3431"
output: github_document
date: "2022-11-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r}
library(tidyverse)
library(modelr)
```

**Problem 2** 

```{r}

crimes_df=
  read_csv("hw6_data/homicide-data.csv") %>% 
  unite("city_state", c("city", "state"), sep = ", ") %>% 
  mutate(solved = ifelse(disposition == "Closed by arrest", 1, 0), 
         victim_race = ifelse(victim_race != "White", "Black", "White"), 
         victim_race = fct_relevel(victim_race, "White", "Black"),
         victim_age = as.numeric(victim_age)) %>% 
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")))

```

Logistic regression with Baltimore 

```{r}
balt_regression=
  crimes_df %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(solved ~ victim_sex + victim_race + victim_age, data = ., family = binomial)

broom::tidy(balt_regression) %>% 
  mutate(or = exp(estimate), 
        lower_CI = exp(estimate - 1.96*std.error), 
         upper_CI = exp(estimate + 1.96*std.error)) %>% 
  filter(term == "victim_sexMale") %>% 
  select(or, lower_CI, upper_CI) %>% 
  knitr::kable(digits = 3)

```

The estimated odds of a crime being solved for a male victim is 0.412 times the estimated odds of a crime being solved for a female victim. We are 95% confident that the true odds ratio lies between the 0.315 and 0.537.  

```{r}
all_cities= 
  crimes_df %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(logit_solve = map(data, ~glm(solved ~ victim_sex + victim_race + victim_age, 
                                      family = binomial, data = .x)), 
         logit_solve = map(logit_solve, broom::tidy)) %>% 
  select(-data) %>% 
  unnest() %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(or = exp(estimate), 
         lower_CI = exp(estimate - 1.96*std.error), 
         upper_CI = exp(estimate + 1.96*std.error), 
         city_state = fct_reorder(city_state, estimate)) %>% 
  select(city_state, or, lower_CI, upper_CI)  
  
  all_cities %>% 
  ggplot(aes(x = city_state, y = or)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = lower_CI, ymax = upper_CI)) + 
  coord_flip() + 
  labs(title = "Odds for solving crimes with male victims compared to crimes with female victims among different cities", 
       y = "Odds ratio", 
       x = "City")
```

The plot demonstrates that most cities have a point estimate below 1, with only Albuquerque, NM, New Orleans, L, and Stockton, CA having an odds ratio greater than 1, indicating that in these cities the odds of a male victim crime being solved is higher than a female victim crime. 

**Problem 3** 


```{r}
birthweight_df = 
  read_csv("hw6_data/birthweight.csv") %>% 
  janitor::clean_names() 

skimr::skim(birthweight_df)$n_missing

bwt_cleaned =
  birthweight_df %>%
  mutate(babysex = recode(babysex,'1' = 'male', '2' = 'female'),
         babysex = factor(babysex, levels = c('male', 'female')),
         frace = recode(frace,
                        '1' = 'White',
                        '2' = 'Black',
                        '3' = 'Asian',
                        '4' = 'Puerto Rican',
                        '8' = 'Other',
                        '9' = 'Unknown'), 
         frace = factor(frace, levels = c('White', 'Black', 'Asian', 'Puerto Rican', 'Other')),
         malform = recode(malform, '0' = 'absent', '1' = 'present'),
         malform = factor(malform, levels = c('absent', 'present')), 
         mrace = recode(mrace,
                        '1' = 'White',
                        '2' = 'Black',
                        '3' = 'Asian',
                        '4' = 'Puerto Rican',
                        '8' = 'Other'), 
         mrace = factor(mrace, levels = c('White', 'Black', 'Asian', 'Puerto Rican', 'Other')))
```

Doing a regression model for birthweight. 

According to the 2022 study by Shaohua et. al., the biggest influences for birthweight is maternal weight gain, gestational weeks, and mothers smoking status. There is also research done by Universities such as Stanford indicating that there exists racial disparities in birthweight which is why I chose to include race in the regression model as well.  

```{r}
bwt_regression =
  lm(bwt ~ bhead + blength  + mrace + mheight + wtgain + smoken + gaweeks, 
     data = bwt_cleaned)

bwt_model=
bwt_cleaned %>% 
  add_predictions(bwt_regression) %>% 
  add_residuals(bwt_regression) 

bwt_model %>% 
  ggplot(aes(x = bwt, y = resid, color= resid)) +
  geom_point(alpha = 0.5) +
  labs(x = "Fitted values",
    y = "Residuals",
    title = "Fitted Values vs Residuals")
```


Comparing model to two others 

```{r}
model_1= lm(bwt ~ blength + gaweeks, data=bwt_cleaned)

model_2= lm(bwt ~ bhead + blength + babysex +
              bhead * blength + 
              bhead * babysex + 
              blength * babysex + 
              bhead * blength * babysex, data= bwt_cleaned)
cv_df = 
  crossv_mc(bwt_cleaned, 100) 

cv_df = cv_df %>% 
  mutate(
    model_0 = map(train, ~lm(bwt ~ smoken + wtgain + bhead + blength + mrace + gaweeks, data = .)),
    model_1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .)),
    model_2 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * bhead + bhead * blength * babysex, data = .)),
  ) %>% 
  mutate(
    rmse_model_0 = map2_dbl(model_0, test, ~rmse(model = .x, data = .y)),
    rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_model2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y))
  )

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse, fill = model)) + 
  geom_violin() +
  labs(
    x = "Model",
    y = "RMSE",
    title = "The distribution of RMSE values for each model"
  ) +
  scale_x_discrete(labels=c("model0" = "Model 0", "model1" = "Model 1",
                              "model2" = "Model 2"))

```



